SaPaFigures

### 2022-03-15 R/PaperFigures.Rmd
added aggregate size distribution figures for mutants, both dots and violin plots

```{r figure 1}
#Figure 1A CFU data wt
#####
#CFU data from Carolyn
CFUdata<-read.csv("/Users/jupabago/Documents/Whiteley/PROJECTS/SaPa Chronic Wounds/Data/From Carolyn/CFU_wound_All_dataTidy.csv",header = TRUE)
CFUdata$Condition<-as.factor(CFUdata$Condition)
   CFUdata$Day<-as.factor(CFUdata$Day)
   CFUdata$Species<-as.factor(CFUdata$Species)
   CFUdata$Strain<-as.factor(CFUdata$Strain)
CFUdata$Condition <- factor(CFUdata$Condition, levels = c("mono", "co-wt", "co-pqsL"))
CFUstats<-CFUdata%>%group_by(Species,Condition,Strain,Day) %>% mutate(MeanCFU = mean(CFU), SECFU = std.error(CFU))
CFUstats$Condition <- factor(CFUstats$Condition, levels = c("mono", "co-wt", "co-pqsL"))

@@

BiomassDataWt = BiomassData%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono") %>% filter(TimePoint == "Day 4" )
biomassWTData = BiomassDataStats%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono") %>% filter(TimePoint == "Day 4" )
#Carolyn wanted to play with the data so here it is:
write.csv(BiomassDataWt,"/Users/jupabago/Documents/Whiteley/PROJECTS/SaPa Chronic Wounds/Data/CSV exports/BiomassWT.csv", row.names = T)

@@

PlotBiomassPoints<- function(){
  ggplot()+
    geom_jitter(data = BiomassDataWt,aes(x=Species,y=Biomass, color = Culture),size=3,position = position_jitterdodge(jitter.height = 0,jitter.width = 0.2, dodge.width = .9))+
    geom_errorbar(data = biomassWTData, aes(x=Species,ymin=(MeanBiomass), ymax = (MeanBiomass), group = Culture)
                ,width = .4, size=.5,position = position_dodge(width = .9))+
    scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)),
                  limits = c(100, 10e7), expand = expand_scale(mult = c(0, 0)))+
    scale_color_grey(labels = c("Mono-culture","Co-culture"))+
    labs(x = "",y = bquote(paste("Biomass per image (", mu*"m"^3*")")))+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5),strip.text = element_text(size = 9, face = "italic",margin = margin(.1,0,.1,0, "cm")),
          strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"),
          axis.title.x = element_text(margin = margin(0,0,0,0),size=13),axis.text.x = element_text(face = "italic",margin = margin(1,0,0,0),size=13),
          axis.title.y = element_text(margin = margin(0,4,0,0),size=13),axis.text.y = element_text(margin = margin(0,0,2,0),size=11))
}
PlotBiomassPoints()
#####

@@

>>>>

```{r figure 1 and 3}
#Figure 1A CFU data wt
#####
#CFU data from Carolyn
CFUdata<-read.csv("/Users/jupabago/Documents/Whiteley/PROJECTS/SaPa Chronic Wounds/Data/From Carolyn/CFU_wound_All_dataTidy.csv",header = TRUE)
CFUdata$Condition<-as.factor(CFUdata$Condition)
   CFUdata$Day<-as.factor(CFUdata$Day)
   CFUdata$Species<-as.factor(CFUdata$Species)
   CFUdata$Strain<-as.factor(CFUdata$Strain)
CFUdata$Condition <- factor(CFUdata$Condition, levels = c("mono", "co-wt", "co-pqsL"))
CFUstats<-CFUdata%>%group_by(Species,Condition,Strain,Day) %>% mutate(MeanCFU = mean(CFU), SECFU = std.error(CFU))
CFUstats$Condition <- factor(CFUstats$Condition, levels = c("mono", "co-wt", "co-pqsL"))

@@

BiomassDataWt = BiomassData%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono") %>% filter(TimePoint == "Day 4" )
BiomassDataMut = BiomassData%>% filter(Culture == "co")  %>% filter(TimePoint == "Day 4" )
biomassWTData = BiomassDataStats%>% filter(Condition == "Sa mono" |Condition == "wt co"|Condition == "wt mono") %>% filter(TimePoint == "Day 4" )
biomassMutData = BiomassDataStats%>% filter(Culture == "co")  %>% filter(TimePoint == "Day 4" )

#Carolyn wanted to play with the data so here it is:
write.csv(BiomassDataWt,"/Users/jupabago/Documents/Whiteley/PROJECTS/SaPa Chronic Wounds/Data/CSV exports/BiomassWT.csv", row.names = T)
write.csv(HistReplicateSummary,"/Users/jpb/Library/Mobile Documents/com~apple~CloudDocs/Documents/Whiteley/PROJECTS/SaPa Chronic Wounds/Data/CSV exports/ReplicateData.csv", row.names = T)
write.csv(HistConditionSummary,"/Users/jpb/Library/Mobile Documents/com~apple~CloudDocs/Documents/Whiteley/PROJECTS/SaPa Chronic Wounds/Data/CSV exports/ConditionData.csv", row.names = T)
write.csv(HistCondRegionSum,"/Users/jpb/Library/Mobile Documents/com~apple~CloudDocs/Documents/Whiteley/PROJECTS/SaPa Chronic Wounds/Data/CSV exports/RegionData.csv", row.names = T)

@@

PlotBiomassPoints<- function(){
  ggplot()+
    geom_jitter(data = BiomassDataWt,aes(x=Species,y=Biomass, color = Culture),size=3,position = position_jitterdodge(jitter.height = 0,jitter.width = 0.2, dodge.width = .9))+
    geom_errorbar(data = biomassWTData, aes(x=Species,ymin=(MeanBiomass), ymax = (MeanBiomass), group = Culture)
                ,width = .4, size=.5,position = position_dodge(width = .9))+
    scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)),
                  limits = c(100, 10e7), expand = expand_scale(mult = c(0, 0)))+
    scale_color_grey(labels = c("Mono-culture","Co-culture"))+
    labs(x = "",y = bquote(paste("Biomass per image (", mu*"m"^3*")")))+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5),strip.text = element_text(size = 9, face = "italic",margin = margin(.1,0,.1,0, "cm")),
          strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"),
          axis.title.x = element_text(margin = margin(0,0,0,0),size=13),axis.text.x = element_text(face = "italic",margin = margin(1,0,0,0),size=13),
          axis.title.y = element_text(margin = margin(0,4,0,0),size=13),axis.text.y = element_text(margin = margin(0,0,2,0),size=11))
}
PlotBiomassPoints()

PlotBiomassPointsMutants<- function(){
  ggplot()+
    geom_jitter(data = BiomassDataMut,aes(x=Species,y=Biomass, color = Strain),size=3,position = position_jitterdodge(jitter.height = 0,jitter.width = 0.2, dodge.width = .9))+
    geom_errorbar(data = biomassMutData, aes(x=Species,ymin=(MeanBiomass), ymax = (MeanBiomass), group = Strain)
                ,width = .4, size=.5,position = position_dodge(width = .9))+
    scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)),
                  limits = c(1, 10e7), expand = expand_scale(mult = c(0, 0)))+
    scale_color_brewer(palette = "Set1",
      labels = c(bquote(paste(italic('S. aureus + P. aeruginosa '))),
                                bquote(paste(italic('S. aureus + P. aeruginosa '*Delta*"pqsL"))), 
                                bquote(paste(italic('S. aureus + P. aeruginosa '*Delta*"phz")))))+

    labs(x = "",y = bquote(paste("Biomass per image (", mu*"m"^3*")")), color = "Condition")+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5),strip.text = element_text(size = 9, face = "italic",margin = margin(.1,0,.1,0, "cm")),
          strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"),
          axis.title.x = element_text(margin = margin(0,0,0,0),size=13),axis.text.x = element_text(face = "italic",margin = margin(1,0,0,0),size=13),
          axis.title.y = element_text(margin = margin(0,4,0,0),size=13),axis.text.y = element_text(margin = margin(0,0,2,0),size=11))
}
PlotBiomassPointsMutantsViolin<- function(){
  ggplot()+
    geom_violin(data = BiomassDataMut,aes(x=Species,y=Biomass, color = Strain))+
    geom_errorbar(data = biomassMutData, aes(x=Species,ymin=(MeanBiomass), ymax = (MeanBiomass), group = Strain)
                ,width = .4, size=.5,position = position_dodge(width = .9))+
    scale_y_log10(breaks = scales::trans_breaks("log10", function(x) 10^x), labels = scales::trans_format("log10", scales::math_format(10^.x)),
                  limits = c(1, 10e7), expand = expand_scale(mult = c(0, 0)))+
    scale_color_brewer(palette = "Set1",
      labels = c(bquote(paste(italic('S. aureus + P. aeruginosa '))),
                                bquote(paste(italic('S. aureus + P. aeruginosa '*Delta*"pqsL"))), 
                                bquote(paste(italic('S. aureus + P. aeruginosa '*Delta*"phz")))))+

    labs(x = "",y = bquote(paste("Biomass per image (", mu*"m"^3*")")), color = "Condition")+
    theme_cowplot()+
    theme(plot.title = element_text(hjust = 0.5),strip.text = element_text(size = 9, face = "italic",margin = margin(.1,0,.1,0, "cm")),
          strip.background = element_rect(color="black", fill="white", size=.5, linetype="solid"),
          axis.title.x = element_text(margin = margin(0,0,0,0),size=13),axis.text.x = element_text(face = "italic",margin = margin(1,0,0,0),size=13),
          axis.title.y = element_text(margin = margin(0,4,0,0),size=13),axis.text.y = element_text(margin = margin(0,0,2,0),size=11))
}
PlotBiomassPointsMutants()
PlotBiomassPointsMutantsViolin()
#####

@@

PlotHistSumFinalStrainsViolin<-function(rep.df,cond.df,region.df, y_var, colorStrain){#doesn't include region
ggplot()+
    geom_violin(data = rep.df %>% filter(TimePoint=="Day 4"),
                scale = "width", trim = F,
                aes(x=as.factor(LogBin),y=.data[[y_var]], color =.data[[colorStrain]]))+
    geom_point(data = region.df%>% filter(TimePoint=="Day 4"),
               aes(x=as.factor(LogBin),y=.data[[y_var]], color =.data[[colorStrain]],shape = Region),
               size=5, position = position_dodge(width = 1) )+
    geom_errorbar(data = cond.df%>% filter(TimePoint=="Day 4"),
               aes(x=as.factor(LogBin),ymin=.data[[y_var]],ymax=.data[[y_var]], group =.data[[colorStrain]]),width = .8,position = position_dodge(width = 1) )+
    facet_grid(.~Species)+
    scale_shape_manual(values=c(16, 1))+
    scale_color_brewer(palette = "Set1",
                       labels = c(bquote(paste(italic('S. aureus + P. aeruginosa '))),
                                bquote(paste(italic('S. aureus + P. aeruginosa '*Delta*"pqsL"))), 
                                bquote(paste(italic('S. aureus + P. aeruginosa '*Delta*"phz")))))+
    scale_x_discrete(labels = c("Planktonic", "5-10", "10-100", "100-1000", ">1000"))+
    labs(y = paste("Frequency (%)"),x = bquote(paste("Aggregate Volume (", mu*"m"^3*")")), color = "Condition")+
    theme_cowplot()+
    panel_border() +
    theme(plot.title = element_text(hjust = 0.5), 
        strip.text = element_text(size = 11, face = "italic",margin = margin(.1,0,.1,0, "cm")),#this is for the facet text
        strip.background = element_rect(color="black", fill="white", size=1, linetype="solid"))#facet background
}#only difference between these two should be "scale_color_grey
PlotHistSumFinalStrainsViolin(HistReplicateSummary%>% filter(Culture =="co"),
            HistConditionSummary%>% filter(Culture =="co"),
            HistCondRegionSum%>% filter(Culture =="co"),
            "NormalizedFrequency","Strain")
